HEP Software Foundation Community White Paper Working Group -- Training, Staffing and Careers

### 2018-06-22 CWP/papers/HSF-CWP-2017-02_training/latex/cwp-wg-training-careers.tex
rewrite

>>>>

In the context of web-based training, if the HSF helps to constitute a living
collection of online tutorials, we could organize regular events such as
a ``Tutorial of the month'', or some sort of ``like'' system. The
best authors must be recognized, so that they can showcase their most popular
online tutorials, just the same as their publications.
